Har en persons høyde innvirkning på lønnen?

### 2020-10-11 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
Skjulte regresjon-chunks

```{r enkel_regresjon, echo=T}
summary(lm(inntekt ~ height_cm, 
           data = heights))

@@

```{r reg_educ, echo=T}
summary(lm(inntekt ~ education, 
           data = heights))

@@

```{r komplett_reg, echo=T}
summary(lm(inntekt ~ education + height_cm + sex + weight + afqt + marital,
           data = heights))

>>>>

```{r enkel_regresjon, echo=F}
summary(lm(inntekt ~ height_cm, 
           data = heights))

@@

```{r reg_educ, echo=F}
summary(lm(inntekt ~ education, 
           data = heights))

@@

```{r komplett_reg, echo=F}
summary(lm(inntekt ~ education + height_cm + sex + weight + afqt + marital,
           data = heights))
